%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[russian]{babel}
\usepackage{hyperref}
\newcommand{\hreftext}[1]{\underline{\textit{#1}}}

\name{Denis Kutukov}
\address{\href{mailto:mail@dskut.ru}{\hreftext{mail@dskut.ru}} \\ 
%\href{http://dskut.ru}{\hreftext{http://dskut.ru}} \\ 
Moscow, Russia
}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bauman Moscow State Technical University} \hfill {\em 2005~--- 2011} \\
Department: Informatics and management systems \\ 
Section: Software engineering and information technologies \\
Master of science \\
Diploma thesis: <<Online news incremental clustering method>> \\
Avg. grade: 4.6

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Yandex}{July 2011~--- present}{Software developer}{Moscow}

April 2013~--- present: Development of Yandex.Mail service, \href{http://mail.yandex.com}{\hreftext{http://mail.yandex.com}}
\item Working on infrastructure projects for service scalability, reliability and perfomance.
\item Development of distributed backend service for retrieving, pre-processing and enhancing message content (i.e. adding meta-data, phishing check, parsing attachments).
\item Development of distributed backend service for asynchronous batch message operations (i.e. labeling very large number of emails).
\item Integrating Yandex.Mail with other Yandex-services.
\item Integration of Javascript interpretator engine on backend.
\item Collaboration with product managers, support specialists, systems administrators and QA engineers. \item Implementing backend-parts for new features in the service, fixing bugs, improving bottle-necks and tuning perfomance of backend.
\item Interviewing candidates.
\item Technologies: C++, python, Javascript, bash/awk, RHEL, Apache Zookeeper, PostgreSQL, Tracemonkey.

Public speech on internals of asynchronous message operations service (in Russian): \\ \href{https://events.yandex.ru/lib/talks/2221/}{\hreftext{https://events.yandex.ru/lib/talks/2221/}}
\\ 

July 2011~--- April 2013: Development of Yandex.News service, \href{http://news.yandex.ru}{\hreftext{http://news.yandex.ru}}
\item Improving news documents annotation and clustering algorithms, both in quality and perfomance.

\item Implementation of using additional data and various word dictionaries in algorithms, implementation of machine learning methods for precision and recall improvements.

\item Evaluation metrics development for recognizing the inner quality of generated news stories.

\item Improvements and refactoring in the whole service architecture design, legacy code maintenance.

\item Development of ancillary scripts and tools for analysis of service functioning.

\item Introduction of unit-testing practice in the team; coverage of the code of my personal responsibility; implementation of a continuous integration instance for automatic algorithms quality metrics monitoring.

\item Technologies: ะก++, perl, python, XML/XSL/JSON/ProtoBuf, bash/awk, FreeBSD/Ubuntu, 
LevelDB.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Devoteam Teligent}{April 2011~--- June 2011}{Software engineer}{Moscow}

\item Design and development of a distributed server application for audio and videoconferences, 
using company's proprietary distributed platform Teligent P90. 

\item Implementation of DTMF handlers and IVR voice messages playback and recording.

\item Development of unit tests (CppUnit), integration tests (python) and a tool for stress testing (C++).

\item Technologies: ะก++, python, bash, RHEL, SIP/SDP/RTP protocols.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{RAA SpetsTekhnika}{February 2010~--- February 2011}{Software engineer}{Moscow}

\item Building software systems destined for theoretical study and practice training of military aircraft pilots.

\item Design and implementation software units for training process management from the trainer's 
workstation and trainee's actions evaluation.

\item Integraion of logging subsystem into trainer's application.

\item Maintenance and rework of application for theoretical study of students and centralized knowledge testing
(a distributed application for use in a computer classroom).

\item Technologies: C\# + managed C++, .NET 3.5, WPF, ADO, Linq, MS SQL Server.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{API}{September 2009~--- January 2010}{Software developer}{Moscow}
\item Development of prototype of mass-media monitoring and analysis system in different regions 
of Russian Federation.

\item Implementation of interface components.

\item Development of SQL stored procedures and database communication unit in the application.

\item Technologies: C\#, .NET 3.5, WPF, MS SQL Server.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical skills}

%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
\textbf{Programming languages:} \\
Strong: C, C++ (STL, boost, C++11), python2.*, perl, bash, Javascript, C\# (.NET) \\
Basic: JavaSE, Erlang, Scala \\
\textbf{DBMS:} \\
PostgreSQL, Oracle, Apache Zookeeper, MS SQL Server, MongoDB, LevelDB \\
\textbf{IDE:} \\
QtCreator, Eclipse, MS Visual Studio \\
\textbf{Tools:} \\
svn, git, JIRA, Redmine, vim, gdb, valgrind, oprofile, gperftools, make, cmake, tcpdump/wireshark, awk, sed \\
\textbf{Operating systems:} \\
UNIX (FreeBSD, Debian/Ubuntu, Arch Linux, RHEL), Windows \\
\textbf{Design patterns:} \\
Go4 (Bridge/Factory/Observer), J2EE(DAO/CompositeEntity), MVC \\
\textbf{Other:} \\
Concurrent programming experience (shared memory, actor model); \\
strong theoretical background (basic data structures, algorithms complexity, 
machine learing, artificial intelligence); \\
experience in building distributed systems; \\
ability to write useful unit tests.
%\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
English & Advanced (fluent) \\
German & C1 (strong level) \\
Russian & native 
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Courses and certificates}
\begin{itemize}
\item Brainbench C++ Master (\href{http://www.brainbench.com/content/transcript/topicdetail.do?testid=12320176}{\hreftext{Public transcript}})

\item Deutsch als Fremdsprache (TestDAF)

\item MOOCs at \href{http://coursera.org}{\hreftext{Coursera}}: \href{https://www.coursera.org/user/i/56a312ee9fc52bd72c3e7d5ab4399016}{\hreftext{my profile}} with current and finished courses

\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------

\begin{rSection}{Hobbies}
Sports (boxing, fitness), literature.
\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
